Kids stove grades and usage summary

### 2020-03-26 stove_grade_usage_summary.Rmd
data cleaning/merging updates

---
title: "Kids stove grades and usage summary"
author: "Ethan Walker"
date: "Started 15 Jan 2020, Updated 16 March 2020"
output: pdf_document 
---

@@

```{r}
# Load data
stove_grades_clean <- read_rds("Output/stove_grades_clean.rds")
stove_use_clean <- read_rds("Output/stove_use_clean.rds")
kids_linked_ids <- read_rds("Output/kids_linked_ids.rds") 
demographics_clean <- read_rds("Output/demographics_clean.rds")
pm_clean <- read_rds("Output/pm_clean.rds")
```

@@

```{r}
## Look further into NA values? ##
stove_grade_summary <- stove_grades_clean %>% 
  #filter(winter_id == 1 & treatment == "Placebo") %>% 
  select(area, home, stove_grade, winter_id) %>% 
  #filter(!is.na(stove_grade)) %>% 
  group_by(area, winter_id, stove_grade) %>% 
  distinct(home) %>% 
  summarize(n()) %>% 
  filter(!is.na(stove_grade))
kable(stove_grade_summary, align = "c")

@@

```{r}
# Generate random sample of stoves to re-grade and validate grading methods

@@

```{r, include=FALSE}
## 18 homes with grades from 2 winters
## 4 of the homes were assigned different grades in each winter
### Was there an upgrade/downgrade to the stove? Check for comments/notes.

@@

```{r, include=FALSE}
# Summarize numeric vars
stove_use_summary <- stove_use_clean %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  group_by(area) %>% 
  summarize("N" = n(),
            "Mean Cords" = mean(wood_cords, na.rm = TRUE),
            "SD Cords" = sd(wood_cords, na.rm = TRUE),
            "Min Cords" = min(wood_cords, na.rm = TRUE), 
            "Median Cords" = median(wood_cords, na.rm = TRUE), 
            "Max Cords" = max(wood_cords, na.rm = TRUE))
kable(stove_use_summary, digits = 1, align = "c")

@@

```{r}
stove_grade_plot <- stove_grades_clean %>% 
  filter(winter_id == 1) %>% 
  select(area, stove_grade) %>% 
  filter(!is.na(stove_grade)) %>% 
  ggplot() +
    geom_bar(aes(stove_grade, fill = area)) +
    theme_minimal() +
    labs(title = "Stove grades") +
    theme(axis.text.x = element_text(size = 16, colour = "black", 
                                     angle = 40, vjust = 0.7, hjust = 0.7),
          axis.text.y = element_text(size = 16, colour = "black"),
          title = element_text(size = 18, colour = "black"),
          legend.text = element_text(size = 14, colour = "black"),
          legend.title = element_text(size = 16, colour = "black"),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(),
          panel.grid = element_blank()) +
    scale_fill_manual(values = jv_palette)
stove_grade_plot
```

```{r}
stove_use_data <- read_rds("Output/stove_use_clean.rds") %>% 
  mutate(wood_cords = as.factor(wood_cords))

stove_use_plot_function <- function(data, variable) {

stove_use_plot <- data %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  select(area, variable) %>% 
  rename(plot_var = variable) %>% 
  #na.exclude() %>% 
  ggplot() +
    geom_bar(aes(plot_var, fill = area)) +
    theme_minimal() +
    labs(title = variable) +
    theme(axis.text.x = element_text(size = 16, colour = "black", 
                                     angle = 40, vjust = 0.7, hjust = 0.7),
          axis.text.y = element_text(size = 16, colour = "black"),
          title = element_text(size = 18, colour = "black"),
          legend.text = element_text(size = 14, colour = "black"),
          legend.title = element_text(size = 16, colour = "black"),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(),
          panel.grid = element_blank()) +
    scale_fill_manual(values = jv_palette)
stove_use_plot

@@

stove_use_plot_function(stove_use_data, "burn_level")
stove_use_plot_function(stove_use_data, "wood_type")
stove_use_plot_function(stove_use_data, "wood_collect")
stove_use_plot_function(stove_use_data, "wood_collect_method")
stove_use_plot_function(stove_use_data, "wood_cords")
```

```{r}
#### Abstract/manuscript tables ####

@@

```{r, include=FALSE}
# Summarize numeric vars
kids_use <- stove_use_filtered %>%  
  #distinct(home, .keep_all = TRUE) %>%  
  group_by(area) %>% 
  summarize("Mean" = mean(wood_cords, na.rm = TRUE), 
            "SD" = sd(wood_cords, na.rm = TRUE),
            "min" = min(wood_cords, na.rm = TRUE), 
            "med" = median(wood_cords, na.rm = TRUE), 
            "max" = max(wood_cords, na.rm = TRUE))
kable(kids_use, digits = 1, align = "c")

>>>>

---
title: "Kids stove grades and usage summary"
author: "Ethan Walker"
date: "Started 15 Jan 2020, Updated 25 March 2020"
output: pdf_document 
---

@@

```{r}
# Load data
stove_grades_clean <- read_rds("Output/stove_grades_clean.rds") 
stove_use_clean <- read_rds("Output/stove_use_clean.rds")
kids_linked_ids <- read_rds("Output/kids_linked_ids.rds") 
demographics_clean <- read_rds("Output/demographics_clean.rds")
#pm_clean <- read_rds("Output/pm_clean.rds")
```

@@

```{r}
## Look further into NA values? ##
stove_grade_summary <- stove_grades_clean %>% 
  #filter(winter_id == 1 & treatment == "Placebo") %>% 
  select(area, home, stove_grade, winter_id) %>% 
  #filter(!is.na(stove_grade)) %>% 
  group_by(area, winter_id, stove_grade) %>% 
  distinct(home) %>% 
  summarize(n()) %>% 
  filter(!is.na(stove_grade))
#kable(stove_grade_summary, align = "c")

@@

```{r, eval=FALSE}
# Generate random sample of stoves to re-grade and validate grading methods

@@

```{r, include=FALSE, eval=FALSE}
## 18 homes with grades from 2 winters
## 4 of the homes were assigned different grades in each winter
### Was there an upgrade/downgrade to the stove? Check for comments/notes.

@@

```{r, include=FALSE, eval=FALSE}
# Summarize numeric vars
stove_use_summary <- stove_use_clean %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  group_by(area) %>% 
  summarize("N" = n(),
            "Mean Cords" = mean(wood_cords, na.rm = TRUE),
            "SD Cords" = sd(wood_cords, na.rm = TRUE),
            "Min Cords" = min(wood_cords, na.rm = TRUE), 
            "Median Cords" = median(wood_cords, na.rm = TRUE), 
            "Max Cords" = max(wood_cords, na.rm = TRUE))
kable(stove_use_summary, digits = 1, align = "c")

@@

```{r}
stove_grade_filtered <- stove_grades_clean %>% 
  arrange(area, home, winter_id) %>% 
  group_by(home) %>% 
  mutate(stove_grade = if_else(is.na(stove_grade), lead(stove_grade), stove_grade)) %>% 
  ungroup()

stove_grade_plot <- stove_grade_filtered %>% 
  filter(winter_id == 1) %>% 
  select(area, stove_grade) %>% 
  filter(!is.na(stove_grade)) %>% 
  ggplot() +
    geom_bar(aes(stove_grade, fill = area)) +
    theme_minimal() +
    labs(title = "Stove grades") +
    theme(axis.text.x = element_text(size = 16, colour = "black", 
                                     angle = 40, vjust = 0.7, hjust = 0.7),
          axis.text.y = element_text(size = 16, colour = "black"),
          title = element_text(size = 18, colour = "black"),
          legend.text = element_text(size = 14, colour = "black"),
          legend.title = element_text(size = 16, colour = "black"),
          axis.title.y = element_blank(),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(),
          panel.grid = element_blank()) +
    scale_fill_manual(values = jv_palette)
stove_grade_plot
```

```{r}
stove_use_data <- read_rds("Output/stove_use_clean.rds") %>% 
  mutate(wood_cords = as.factor(wood_cords),
         burn_level = factor(burn_level,
                             levels = c("No burning", "Light burning",
                                        "Average burning", "Heavy burning")))

stove_use_plot_function <- function(data, var, title_label, y_label) {

  stove_use_plot <- data %>% 
  filter(winter_id == 1) %>% 
  select(area, var) %>% 
  rename(plot_var = var) %>% 
  filter(!is.na(plot_var)) %>% 
  ggplot() +
    geom_bar(aes(plot_var, fill = area)) +
    theme_minimal() +
    theme(axis.text.x = element_text(size = 16, colour = "black", 
                                     angle = 40, vjust = 0.7, hjust = 0.7),
          axis.text.y = element_text(size = 16, colour = "black"),
          title = element_text(size = 20, colour = "black"),
          legend.text = element_text(size = 18, colour = "black"),
          legend.title = element_text(size = 18, colour = "black"),
          axis.title.y = element_text(size = 18, colour = "black"),
          axis.title.x = element_blank(),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(),
          panel.grid = element_blank()) +
    labs(title = title_label) +
    ylab(y_label) +
    scale_fill_manual(values = jv_palette)
  stove_use_plot

@@

stove_use_plot_function(stove_use_data, "burn_level", "Burn level", "count")
stove_use_plot_function(stove_use_data, "wood_type", "Wood type", "count")
stove_use_plot_function(stove_use_data, "wood_collect", "Wood collection", "count")
stove_use_plot_function(stove_use_data, "wood_collect_method", "Wood collect method", "count")
stove_use_plot_function(stove_use_data, "wood_cords", "Wood cords burned", "count")
```

```{r, eval=FALSE}
#### Abstract/manuscript tables ####

@@

```{r, include=FALSE, eval=FALSE}
# Summarize numeric vars
kids_use <- stove_use_filtered %>%  
  #distinct(home, .keep_all = TRUE) %>%  
  group_by(area) %>% 
  summarize("Mean" = mean(wood_cords, na.rm = TRUE), 
            "SD" = sd(wood_cords, na.rm = TRUE),
            "min" = min(wood_cords, na.rm = TRUE), 
            "med" = median(wood_cords, na.rm = TRUE), 
            "max" = max(wood_cords, na.rm = TRUE))
kable(kids_use, digits = 1, align = "c")
